Interval Probability for Fuzzy Quantum Theories

### 2016-07-02 prob.tex
"Georges-Louis Leclerc, Comte de Buffon.pdf" Updated...
prob.tex \section{Proof of Quantum Interval-valued Probability Measures} updated....

@@

\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
events~$\events$, a collection of intervals~$\mathscr{I}$, and
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
\qed\end{lemma}
\end{document}

>>>>

In order to simplify the notation, consider the following definition
for interval-valued probability measures.

\begin{definition}Given a Hilbert space~$\Hilb$ with the set of
quantum events~$\events$, a collection of intervals~$\mathscr{I}$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
Let $l:\events\rightarrow\left[0,1\right]$ and $r:\events\rightarrow\left[0,1\right]$
such that $\left[l\left(P\right),r\left(P\right)\right]=\bar{\mu}\left(P\right)$.\qed\end{definition}

@@

\begin{lemma}Given a Hilbert space~$\Hilb$ with the set of quantum
events~$\events$, a collection of intervals~$\mathscr{I}$, and
a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
For projection operators $P_{1}$ and $P_{2}$, if $P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}$,
then $\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{\ge}{}\bar{\mu}\left(P_{2}\right)$,
where $\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{\ge}{}\left[l_{2},r_{2}\right]$
if and only if $l_{1}\tensor*[_{\mathbb{R}}]{\ge}{}l_{2}$ and $r_{1}\tensor*[_{\mathbb{R}}]{\ge}{}r_{2}$.
The preposing $\mathbb{R}$ represents its an inequality of real numbers
as usual.\qed\end{lemma}

\begin{proof}

\begin{eqnarray*}
 &  & P_{1}\tensor*[_{\mathscr{O}}]{\ge}{}P_{2}\\
 & \Rightarrow & \bar{\mu}\left(P_{1}\right)\subseteq\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)\\
 & \Rightarrow & l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{\ge}{}l\left(P_{2}\right)
\end{eqnarray*}
Similarly, 
\begin{eqnarray*}
 &  & \mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\tensor*[_{\mathscr{O}}]{\le}{}\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\\
 & \Rightarrow & 1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{1}\right)=l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{1}\right)\tensor*[_{\mathbb{R}}]{\le}{}l\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P_{2}\right)=1\tensor*[_{\mathbb{R}}]{-}{}r\left(P_{2}\right)\\
 & \Rightarrow & r\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{\ge}{}r\left(P_{2}\right)
\end{eqnarray*}

\end{proof}
\end{document}
